### 2020-03-16 README.Rmd
final tweaks

bw_predict %>%
  group_by(focal_ID) %>%
  summarise(growth = mean(growth), growth_hat = mean(growth_hat)) %>%
  ggplot(aes(growth, growth_hat)) +
  geom_point(size = 0.5, color = rgb(0,0,0,0.25)) +
  stat_smooth(method = 'lm') +
  geom_abline(slope = 1, intercept = 0) +
  labs(x = "Observed growth in dbh", y = "Predicted growth in dbh")
```

>>>>

bw_predict %>%
  group_by(focal_ID, focal_notion_of_species) %>%
  # Since for the same focal tree all growth & growth_hat values are the same:
  summarise(growth = mean(growth), growth_hat = mean(growth_hat)) %>%
  ggplot(aes(x = growth, y = growth_hat)) +
  geom_point(size = 0.5, color = rgb(0,0,0,0.25)) +
  stat_smooth(method = 'lm') +
  geom_abline(slope = 1, intercept = 0) +
  coord_fixed() + 
  labs(x = "Observed growth in dbh", y = "Predicted growth in dbh")
```
